---
title: "PK Simulations in Modified Patients"
author: "Neha Mehta"
date: "`r Sys.Date()`"
output: html_document
---

```{r normalize_path, include=F, eval=F}
# FOR INTERACTIVE USE
# set this so can normalize wd from Rstudio project and when knitting
# eg if your rmd is in /lab-notebook/<notebook>.Rmd
# it should look like setwd(paste0(getwd(), "/lab-notebook/"))
setwd(paste0(getwd(), "/<PATH>"))
```

```{r libraries}
# required libraries
library("PKPDmisc")
library("ggplot2")
library("dplyr")
library("mlxR")
library("reshape2")
library("knitr")
```

```{r}
knitr::opts_chunk$set(echo=FALSE)
```

# 1. pk profile of 100 mg iv bolus (SD), CL = 0.1 L/hr, V = 1 L
```{r}
adm1 <- list(time=c(0), amount=100)
t1   <- seq(0, 120, by=0.1)
param1   <- c(V=1, Cl=0.1)

res1   <- pkmodel(time = t1, treatment = adm1, parameter = param1)

ggplot(data=res1, aes(x=time, y=cc)) + geom_line(size=1) +
  xlab("time (h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```
## 1a. Patient's clearance decreases by 25%. (PK profile of 100 mg iv bolus (SD), CL = 0.075 L/hr, V= 1 L)
```{r}
adm1a <- list(time=c(0), amount=100)
t1a <- seq(0, 120, by=0.1)
param1a <- c(V=1, Cl=0.075)

res1a <- pkmodel(time = t1a, treatment = adm1a, parameter = param1a)

ggplot(data=res1a, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```
## 1b. Patient's clearance decreases by 50%. (PK profile of 100 mg iv bolus (SD), CL = 0.05 L/hr, V = 1 L)
```{r}
adm1b <- list(time=c(0), amount=100)
t1b <- seq(0, 120, by=0.1)
param1b <- c(V=1, Cl=0.05)

res1b <- pkmodel(time = t1b, treatment = adm1b, parameter = param1b)

ggplot(data=res1b, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```
## 1c. Overlay PK profiles of patient with normal clearance and decreased clearance (PK profile of 100 mg iv bolus (sd), V = 1 L, CL1 = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res1 %>% mutate(profile = "100mg SD"),
                              res1a %>% mutate(profile = "100mg SD, CL = 0.075 L/hr"),
                              res1b %>% mutate(profile = "100mg SD, CL = 0.05 L/hr"))

combined_output %>%
ggplot(aes(x = time, y = cc, color = factor(profile))) +
geom_line() + xlab("time(h)") + ylab("concentration (mg/L)") +
scale_color_discrete(name = "Clearance Changes") + theme_bw() + base_theme()
```

# 2. PK profile of 100 mg iv bolus, LD (t = 0), MD (q= 6 hr), CL = 0.1 L/hr, V = 1 L
```{r}
adm2 <- list(time=seq(0, 120, by = 6), amount=100)
t2 <- seq(0, 120, by=0.1)
param2 <- c(V=1, Cl=0.1)

res2 <- pkmodel(time = t2, treatment = adm2, parameter = param2)

ggplot(data=res2, aes(x=time, y=cc)) + geom_line(size=1) +
        xlab("time (h)") + ylab("concentration (mg/L)") +
        theme_bw() + base_theme()
```
## 2a. Patient's clearance decreases by 25%. (PK profile of 100 mg iv bolus, LD (t=0), MD (q=6hr), CL = 0.075 L/hr, V= 1 L)
```{r}
adm2a <- list(time=seq(0, 120, by = 6), amount=100)
t2a <- seq(0, 120, by=0.1)
param2a <- c(V=1, Cl=0.075)

res2a <- pkmodel(time = t2a, treatment = adm2a, parameter = param2a)

ggplot(data=res2a, aes(x=time, y=cc)) + geom_line(size=1) +
  xlab("time(h)") + ylab("concentration(mg/L)") +
  theme_bw() + base_theme()
```
## 2b. Patient's clearance decreases by 50%. (PK profile of 100 mg iv bolus, LD (t=0), MD (q=6hr), CL = 0.05 L/hr, V= 1 L)
```{r}
adm2b <- list(time=seq(0, 120, by = 6), amount = 100)
t2b <- seq(0, 120, by=0.1)
param2b <- c(V=1, Cl=0.05)

res2b <- pkmodel(time = t2b, treatment = adm2b, parameter = param2b)

ggplot(data=res2b, aes(x=time, y=cc)) + geom_line(size=1) +
  xlab("time(h)") + ylab("concentration(mg/L)") +
  theme_bw() + base_theme()
```
## 2c. Overlay PK profiles of patient with normal clearance and decreased clearance (PK profile of 100 mg iv bolus, LD(t=0), MD (q=6hr), V = 1 L, CL = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res2 %>% mutate(profile = "100mg Q6, CL = 0.1 L/hr"),
                              res2a %>% mutate(profile = "100mg Q6, CL = 0.075 L/hr"),
                              res2b %>% mutate(profile = "100mg Q6, CL = 0.05 L/hr"))
combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) + geom_line() +
  xlab("time(h)") + ylab("concentration (mg/L)") +
  scale_color_discrete(name = "Clearance Values") + theme_bw() + base_theme()
```

# 3. PK profile of 100 mg iv bolus, LD (t=0), MD (q=12 hr), CL =0.1 L/hr, V = 1 L
```{r}
adm3 <- list(time=seq(0, 120, by = 12), amount = 100)
t3 <- seq(0, 120, by = 0.1)
param3 <- c(V=1, Cl=0.1)

res3 <- pkmodel(time = t3, treatment = adm3, parameter = param3)

ggplot(data=res3, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```
## 3a. Patient's clearance decreases by 25%. (PK profile of 100 mg iv bolus, LD (t=0), MD (q=12hr), CL = 0.075 L/hr, V= 1 L)
```{r}
adm3a <- list(time=seq(0, 120, by = 12), amount = 100)
t3a <- seq(0, 120, by = 0.1)
param3a <- c(V=1, Cl=0.075)

res3a <- pkmodel(time = t3a, treatment = adm3a, parameter = param3a)

ggplot(data=res3a, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```
## 3b. Patient's clearance decreases by 50%. (PK profile of 100 mg iv bolus, LD (t=0), MD (q=12hr), CL = 0.05 L/hr, V= 1 L)
```{r}
adm3b <- list(time=seq(0, 120, by = 12), amount = 100)
t3b <- seq(0, 120, by = 0.1)
param3b <- c(V=1, Cl=0.05)

res3b <- pkmodel(time = t3b, treatment = adm3b, parameter = param3b)

ggplot(data=res3b, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```
## 3c. Overlay PK profiles of patient with normal clearance and decreased clearance (PK profile of 100 mg iv bolus, LD(t=0), MD (q=12hr), V = 1 L, CL = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res3 %>% mutate(profile = "100mg Q12, CL = 0.1 L/hr"),
                              res3a %>% mutate(profile = "100mg 12, CL = 0.075 L/hr"),
                              res3b %>% mutate(profile = "100mg Q12, CL = 0.05 L/hr"))
combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) + geom_line() +
  xlab("time(h)") + ylab("concentration (mg/L)") +
  scale_color_discrete(name = "Clearance Values") + theme_bw() + base_theme()
```

# 4. PK profile of 100 mg IV bolus, LD (t=0), MD (q=24 hr), CL=0.1 L/hr, V=1L
```{r}
adm4 <- list(time=seq(0, 120, by = 24), amount = 100)
t4 <- seq(0, 120, by = 0.1)
param4 <- c(V=1, Cl=0.1)

res4 <- pkmodel(time= t4, treatment= adm4, parameter= param4)

ggplot(data=res4, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```
## 4a. Patient's clearance decreases by 25%. (PK profile of 100 mg IV bolus, LD (t=0), MD (q=24hr), CL = 0.075 L/hr, V= 1 L)
```{r}
adm4a <- list(time=seq(0, 120, by = 24), amount = 100)
t4a <- seq(0, 120, by = 0.1)
param4a <- c(V=1, Cl=0.075)

res4a <- pkmodel(time = t4a, treatment = adm4a, parameter = param4a)

ggplot(data=res4a, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```
## 4b. Patient's clearance decreases by 50%. (PK profile of 100 mg iv bolus, LD (t=0), MD (q=24hr), CL = 0.05 L/hr, V= 1 L)
```{r}
adm4b <- list(time=seq(0, 120, by = 24), amount = 100)
t4b <- seq(0, 120, by = 0.1)
param4b <- c(V=1. Cl=0.05)

res4b <- pkmodel(time = t4b, treatmet = adm4b, parameter = param4b)

ggplot(data=res4b, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```
## 4c. Overlay PK profiles of patient with normal clearance and decreased clearance
(PK profile of 100 mg iv bolus, LD(t=0), MD (q=24hr), V = 1 L, CL = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res4 %>% mutate(profile = "100mg Q24, CL = 0.1 L/hr"),
                              res4a %>% mutate(profile = "100mg Q24, CL = 0.075 L/hr"),
                              res4b %>% mutate(profile = "100mg Q24, CL = 0.05 L/hr"))

combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) + geom_line() +
  xlab("time(h)") + ylab("concentration(mg/L)") +
  scale_color_discrete(name = "Clearance Values") + theme_bw() + base_theme()
```

# 5. PK profile of 100 mg oral (SD), CL = 0.1 L/hr, V = 1 L, ka = 0.5/hr, F = 0.8
```{r}
adm5 <- list(time=c(0), amount=100)
t5 <- seq(0, 120, by = 0.1)
param5 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res5 <- pkmodel(time = t5, treatment = adm5, parameter = param5)

ggplot(data=res5, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time (h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```
## 5a. Patient's clearance decreases by 25%. (PK profile of 100 mg oral, SD (t=0), CL = 0.075 L/hr, V= 1 L, ka = 0.5/hr, F=0.8)
```{r}
adm5a <- list(time=c(0), amount=100)
t5a <- seq(0, 120, by = 0.1)
param5a <- c(V=1, Cl=0.075, ka=0.5, p=0.8)

res5a <- pkmodel(time = t5a, treatment=adm5a, parameter = param5a)

ggplot(data=res5a, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```
## 5b. Patient's clearance decreases by 50%. (PK profile of 100 mg oral, SD (t=0), CL = 0.05 L/hr, V= 1 L)
```{r}
adm5b <- list(time=c(0), amount=100)
t5b <- seq(0, 120, by = 0.1)
param5b <- c(V=1, Cl=0.05, ka=0.5, p =0.8)

res5b <- pkmodel(time = t5b, treatment = adm5b, parameter = param5b)

ggplot(data=res5b, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```
## 5c. Patient consumes a high fat meal 48 hours after beginning treatment, which reduces bioavailability by 50%.
(PK profile of 100 mg oral (sd), CL = 0.1 L/hr, V = 1 L, ka = 0.5/hr, F = 0.8)
```{r}
dose_times <- seq(0,100,12)
doses <- ifelse(dose_times < 48, 100, 80)
adm5c <- list(time = dose_times, amount = doses)
param5c <- c(V=1, CL =0.1, ka =0.5, p =0.8)

res5c <- pkmodel(time = dose_times, treatment = adm5c, parameter = param5c)

ggplot(data=res5c, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time (h)") + ylab("concentration(mg/L)") +
      theme_bw() + base_theme()
```
## 5d. Overlay plot of patient with decreased clearance and normal clearance.
(PK profile of 100 mg oral, SD (t=0), CL = 1, 0.075, 0.05 L/hr, V=1, Ka = 0.8)
```{r}
combined_output <- bind_rows(res5 %>% mutate(profile = "100mg Q24, CL = 0.1 L/hr"),
                              res5a %>% mutate(profile = "100mg Q24, CL = 0.075 L/hr"),
                              res5b %>% mutate(profile = "100mg Q24, CL = 0.05 L/hr"))

combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) + geom_line() +
  xlab("Time(h)") + ylab("Concentration(mg/L)") +
  scale_color_discrete(name = "Clearance Values") + theme_bw() + base_theme()
```
## 5e. Overlay plot of patient with normal bioavailability and decreased bioavailability
(PK profile of 100 mg oral, SD(t=0), CL = 1 L/hr, Ka = 0.8, 0.4)

# 6. Patient is administered 100 mg oral loading dose and a 100 mg maintenance dose every 6 hours.
### PK profile of 100 mg oral, LD (t=0), MD (q= 6 hr), CL = 0.1 L/hr, V = 1 L, ka = 0.5/hr, F = 0.8
```{r}
adm6 <- list(time=seq(0, 120, by=6), amount=100)
t6 <- seq(0, 120, by = 0.1)
param6 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res6 <- pkmodel(time = t6, treatment = adm6, parameter = param6)

ggplot(data=res6, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time (h)") + ylab("concentration (mg/L)") +
      theme_bw() + base_theme()
```
## 6a. Patient's clearance decreases by 25%.
### PK profile of 100 mg oral, LD (t=0), MD (q= 6 hr), CL = 0.075 L/hr, V= 1 L, ka = 0.5/hr, F=0.8
```{r}
adm5a <- list(time=c(0, 120, by = 6), amount=100)
t5a <- seq(0, 120, by = 0.1)
param5a <- c(V=1, Cl=0.075, ka=0.5, p=0.8)

res5a <- pkmodel(time = t5a, treatment=adm5a, parameter = param5a)

ggplot(data=res5a, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration(mg/L)") +
      theme_bw() + base_theme()
```
## 6b. Patient's clearance decreases by 50%.
### PK profile of 100 mg oral, LD (t=0), MD (q= 6 hr), CL = 0.05 L/hr, V= 1 L, ka = 0.5/hr, F=0.8
```{r}
adm5b <- list(time=c(0, 120, by = 6), amount=100)
t5b <- seq(0, 120, by = 0.1)
param5b <- c(V=1, Cl=0.05, ka=0.5, p=0.8)

res5b <- pkmodel(time=t5b, treatment=adm5b, parameter=param5b)

ggplot(data=res5b, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration(mg/L)") +
      theme_bw() + base_theme()
```
## 6c. Patient consumes a high fat meal 48 hours after beginning treatment, which reduces bioavailability by 50%.
### PK profile of 100 mg oral, LD (t=0), MD (q=6 hr), CL = 1 L/hr, V = 1 L, ka = 0.5/hr, F=0.8
```{r}

```
## 6d. Overlay plot of patient with decreased clearance and normal clearance.
### PK profile of 100 mg oral, LD (t=0), MD (q=6 hr), CL = 1, 0.075, 0.05 L/hr, V = 1 L, ka = 0.5/hr, F=0.8
```{r}
combined_output <- bind_rows(res5 %>% mutate(profile = "100mg Q6, CL = 0.1 L/hr"),
                              res5a %>% mutate(profile = "100mg Q6, CL = 0.075 L/hr"),
                              res5b %>% mutate(profile = "100mg Q6, CL = 0.05 L/hr"))

combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) +
    geom_line() +
      xlab("Time(h)") + ylab("Concentration(mg/L)") +
        scale_color_discrete(name = "Clearance Values") +
          theme_bw() + base_theme()
```
## 6e. Overlay plot of patient with normal bioavailability and decreased bioavailability.
### PK profile of 100 mg oral, LD (t=0), MD (q=6 hr), CL = 1 L/hr, V = 1 L, ka = 0.5/hr, F=0.8, 0.4
```{r}

```

# 7. Patient is administered 100 mg oral loading dose, followed by a maintenance dose of 100 mg every 12 hours.
### PK profile of 100 mg oral, LD (t=0), MD (q=12 hr), CL=0.1 L/hr, V=1L, ka=0.5/hr, F=0.8
```{r}
adm7 <- list(time=seq(0, 120, by = 12), amount = 100)
t7 <- seq(0, 120, by = 0.1)
param7 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res7 <- pkmodel(time = t7, treatment= adm7, parameter = param7)

ggplot(data=res7, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration (mg/L)") +
      theme_bw() + base_theme()
```

  ## 7a. Patient's clearance decreases by 25%.
  ### PK profile of 100 mg oral, LD (t=0), MD (q= 12 hr), CL = 0.075 L/hr, V= 1 L, ka = 0.5/hr, F=0.8
```{r}
adm7a <- list(time=seq(0, 120, by = 12), amount = 100)
t7a <- seq(0, 120, by = 0.1)
param7a <- c(V=1, Cl=0.075, ka=0.5, p=0.8)

res7a <- pkmodel(time = t7a, treatment = adm7a, parameter = param7a)

ggplot(data=res7a, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration(mg/L)") +
      theme_bw() + base_theme()
```

  ## 7b. Patient's clearance decreases by 50%.
  ### PK profile of 100 mg oral, LD (t=0), MD (q=12 hr), CL = 0.05 L/hr, V= 1 L, ka=0.5/hr, F=0.8
```{r}
adm7b <- list(time=seq(0, 120, by = 12), amount = 100)
t7b <- seq(0, 120, by = 0.1)
param7b <- c(V=1, Cl=0.05, ka=0.5, p=0.8)

res7b <- pkmodel(time = t7b, treatment = adm7b, parameter = param7b)

ggplot(data=res7b, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration(mg/L)") +
      theme_bw() + base_theme()
```

  ## 7c. Patient consumes a high fat meal 48 hours after beginning treatment, which reduces bioavailability by 50%.
  ### PK profile of 100 mg oral, LD (t=0), MD (q=12 hr), CL = 1 L/hr, V = 1 L, ka = 0.5/hr, F=0.4
```{r}

```

 ## 7d. Overlay plot of patient with decreased clearances and normal clearance.
 ### PK profile of 100 mg oral, LD (t=0), MD (q=6 hr), CL = 1, 0.075, 0.05 L/hr, V = 1 L, ka = 0.5/hr, F=0.8
```{r}
combined_output <- bind_rows(res7 %>% mutate(profile = "100mg Q12, CL = 0.1 L/hr"),
                              res7a %>% mutate(profile = "100mg Q12, CL = 0.075 L/hr"),
                              res7b %>% mutate(profile = "100mg Q12, CL = 0.05 L/hr"))

combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) +
    geom_line() +
      xlab("Time(h)") + ylab("Concentration(mg/L)") +
        scale_color_discrete(name = "Clearance Values") +
          theme_bw() + base_theme()
```

  ## 7e. Overlay plot of patient with normal bioavailability and decreased bioavailability.
  ### PK profile of 100 mg oral, LD (t=0), MD (q=6 hr), CL = 1 L/hr, V = 1 L, ka = 0.5/hr, F=0.8, 0.4
```{r}

```

# 8. Patient is administered a 100 mg loading dose, followed by a maintenance dose of 100 mg every 24 hours.
### PK profile of 100 mg oral, LD (t=0), MD (q=24 hr), CL = 0.1 L/hr, V=1L, ka=0.5/hr, F=0.8
```{r}
adm8 <- list(time=seq(0, 120, by = 24), amount = 100)
t7 <- seq(0, 120, by = 0.1)
param7 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res8 <- pkmodel(time = t8, treatment= adm8, parameter = param8)

ggplot(data=res8, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration (mg/L)") +
      theme_bw() + base_theme()
```

## 8a. Patient's clearance decreases by 25%.
### PK profile of 100 mg oral, LD (t=0), MD (q= 24 hr), CL = 0.075 L/hr, V= 1 L, ka = 0.5/hr, F=0.8
```{r}
adm8a <- list(time=seq(0, 120, by = 24), amount = 100)
t8a <- seq(0, 120, by = 0.1)
param8a <- c(V=1, Cl=0.075, ka=0.5, p=0.8)

res8a <- pkmodel(time = t8a, treatment = adm8a, parameter = param8a)

ggplot(data=res8a, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration(mg/L)") +
      theme_bw() + base_theme()
```

## 8b. Patient's clearance decreases by 50%.
### PK profile of 100 mg oral, LD (t=0), MD (q= 24 hr), CL = 0.05 L/hr, V= 1 L, ka=0.5/hr, F=0.8
```{r}
adm8b <- list(time=seq(0, 120, by = 24), amount = 100)
t8b <- seq(0, 120, by = 0.1)
param8b <- c(V=1, Cl=0.05, ka=0.5, p=0.8)

res8b <- pkmodel(time = t8b, treatment = adm8b, parameter = param8b)

ggplot(data=res8b, aes(x=time, y=cc)) +
  geom_line(size=1) +
    xlab("time(h)") + ylab("concentration(mg/L)") +
      theme_bw() + base_theme()
```

## 8c. Patient consumes a high fat meal 48 hours after beginning treatment, which reduces bioavailability by 50%.
### PK profile of 100 mg oral, LD (t=0), MD (q=24 hr), CL = 1 L/hr, V = 1 L, ka = 0.5/hr, F=0.4
```{r}

```

## 8d. Overlay plot of patient with decreased clearances and normal clearance.
### PK profile of 100 mg oral, LD (t=0), MD (q=24 hr), CL = 1, 0.075, 0.05 L/hr, V = 1 L, ka = 0.5/hr, F=0.8
```{r}
combined_output <- bind_rows(res8 %>% mutate(profile = "100mg Q24, CL = 0.1 L/hr"),
                              res8a %>% mutate(profile = "100mg Q24, CL = 0.075 L/hr"),
                              res8b %>% mutate(profile = "100mg Q24, CL = 0.05 L/hr"))

combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) +
    geom_line() +
      xlab("Time(h)") + ylab("Concentration(mg/L)") +
        scale_color_discrete(name = "Clearance Values") +
          theme_bw() + base_theme()
```

  ## 7e. Overlay plot of patient with normal bioavailability and decreased bioavailability.
  ### PK profile of 100 mg oral, LD (t=0), MD (q=6 hr), CL = 1 L/hr, V = 1 L, ka = 0.5/hr, F=0.8, 0.4
```{r}

```

# 9. Overlay plots - oral
```{r}
combined_output <- bind_rows(res8 %>% mutate(profile = "100mg Q24"),
                           res7 %>% mutate(profile = "100mg Q12"),
                           res6 %>% mutate(profile= "100mg Q6"),
                           res5 %>% mutate(profile= "100mg SD"))

combined_output %>%
    ggplot(aes(x = time, y = cc, color = factor(profile))) +
    geom_line() + xlab("time(h)") + ylab("concentration (mg/L)") +
    scale_color_discrete(name = "Dosing Regimen") + theme_bw() + base_theme()
```

# 10. Overlay plots - iv
```{r}
combined_output <- bind_rows(res1 %>% mutate(profile = "100mg SD"),
                             res2 %>% mutate(profile = "100mg Q6"),
                             res3 %>% mutate(profile = "100mg Q12"),
                             res4 %>% mutate(profile = "100mg Q24"))


combined_output %>%
  ggplot(aes(x = time, y = cc, color = factor(profile))) +
  geom_line() + xlab("time(h)") + ylab("concentration (mg/L)") +
  scale_color_discrete(name = "Dosing Regimen") + theme_bw() + base_theme()
```

```{r}
devtools::session_info()
```
