---
output: pdf_document
---
```{r libraries}
# required libraries
library("PKPDmisc")
library("ggplot2")
library("mlxR")
library("reshape2")
library("knitr")
library("dplyr")
??mlxR
```

```{r}
knitr::opts_chunk$set(echo=FALSE)
```

# 1. pk profile of 100 mg iv bolus (sd), CL = 0.1 L/hr, V = 1 L
```{r}
# where to start analysis
adm <- list(time=c(0), amount=100)
t   <- seq(0, 120, by=0.1)
param   <- c(V=1, Cl=0.1)

res   <- pkmodel(time = t, treatment = adm, parameter = param)

ggplot(data=res, aes(x=time, y=cc)) + geom_line(size=1) +
  xlab("time (h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

# 2. pk profile of 100 mg iv bolus, ld (t = 0), md (q= 6 hr), cl = 0.1 L/hr, v = 1 L
```{r}
adm2 <- list(time=seq(0, 120, by = 6), amount=100)
t2 <- seq(0, 120, by=0.1)
param2 <- c(V=1, Cl=0.1)

res2 <- pkmodel(time = t2, treatment = adm2, parameter = param2)

ggplot(data=res2, aes(x=time, y=cc)) + geom_line(size=1) +
        xlab("time (h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

# 3. pk profile of 100 mg iv bolus, ld (t=0), md (q=12 hr), cl =0.1 l/hr, v = 1l
```{r}
adm3 <- list(time=seq(0, 120, by = 12), amount = 100)
t3 <- seq(0, 120, by = 0.1)
param3 <- c(V=1, Cl=0.1)

res3 <- pkmodel(time = t3, treatment = adm3, parameter = param3)

ggplot(data=res3, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

# 4. pk profile of 100 mg iv bolus, ld (t=0), md (q=24 hr), cl=0.1 l/hr, v=1l
```{r}
adm4 <- list(time=seq(0, 120, by = 24), amount = 100)
t4 <- seq(0, 120, by = 0.1)
param4 <- c(V=1, Cl=0.1)

res4 <- pkmodel(time= t4, treatment= adm4, parameter= param4)

ggplot(data=res4, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```

# 3. pk profile of 100 mg oral (sd), Cl = 0.1 L/hr, V = 1 L, ka = 0.5/hr, F = 0.8
```{r}
adm5 <- list(time=c(0), amount=100)
t5 <- seq(0, 120, by = 0.1)
param5 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res5 <- pkmodel(time = t5, treatment = adm5, parameter = param5)

ggplot(data=res5, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time (h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

# 4. pk profile of 100 mg oral, ld (t=0), md (q= 6 hr), Cl = 0.1 L/hr, V = 1 L, ka = 0.5/hr, F = 0.8
```{r}
adm6 <- list(time=seq(0, 120, by=6), amount=100)
t6 <- seq(0, 120, by = 1)
param6 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res6 <- pkmodel(time = t6, treatment = adm6, parameter = param6)

ggplot(data=res6, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time (h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

# 5. pk profile of 100 mg oral, ld (t=0), md (q=12 hr), cl=0.1 l/hr, v=1l, ka=0.5/hr, f=0.8
```{r}
adm7 <- list(time=seq(0, 120, by = 12), amount = 100)
t7 <- seq(0, 120, by = 1)
param7 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res7 <- pkmodel(time = t7, treatment= adm7, parameter = param7)

ggplot(data=res7, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

# 6. pk profile of 100 mg oral, ld (t=0), md (q=24 hr), cl = 0.1 l/hr, v=1l, ka=0.5/hr, f=0.8
```{r}
adm8 <- list(time= seq(0, 120, by = 24), amount=100)
t8 <- seq(0, 120, by = 1)
param8 <- c(V=1, Cl=0.1, ka=0.5, p=0.8)

res8 <- pkmodel(time = t8, treatment = adm8, parameter = param8)

ggplot(data=res8, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```

# Overlay plots - oral
```{r}
combined_output <- bind_rows(res8 %>% mutate(profile = "100mg Q24"),
                           res7 %>% mutate(profile = "100mg Q12"),
                           res6 %>% mutate(profile= "100mg Q6"),
                           res5 %>% mutate(profile= "100mg SD"))

combined_output %>%
    ggplot(aes(x = time, y = cc, color = factor(profile))) + 
    geom_line() + xlab("time(h)") + ylab("concentration (mg/L)") +
    scale_color_discrete(name = "Dosing Regimen")
```

# Overlay plots - iv
```{r}
combined_output <- bind_rows(res %>% mutate(profile = "100mg SD"),
                             res2 %>% mutate(profile = "100mg Q6"),
                             res3 %>% mutate(profile = "100mg Q12"),
                             res4 %>% mutate(profile = "100mg Q24"))


combined_output %>%
  ggplot(aes(x = time, y = cc, color = factor(profile))) +
  geom_line() + xlab("time(h)") + ylab("concentration (mg/L)") +
  scale_color_discrete(name = "Dosing Regimen")
```
