---
title: "PK Simulations of 100 mg IV in Patients with Modified CL and F"
author: "Neha Mehta"
date: "`r Sys.Date()`"
output: html_document
---

```{r normalize_path, include=F, eval=F}
# FOR INTERACTIVE USE
# set this so can normalize wd from Rstudio project and when knitting
# eg if your rmd is in /lab-notebook/<notebook>.Rmd
# it should look like setwd(paste0(getwd(), "/lab-notebook/"))
setwd(paste0(getwd(), "/<PATH>"))
```

```{r libraries}
# required libraries
library("PKPDmisc")
library("ggplot2")
library("dplyr")
library("mlxR")
library("reshape2")
library("knitr")
```

```{r}
knitr::opts_chunk$set(echo=FALSE)
```

# *IV FORMULATION*

# 1. PK profile of 100 mg IV bolus administered as a single dose.
##### (PK profile of 100 mg IV bolus (SD), CL = 0.1 L/hr, V = 1 L)
```{r}
adm1 <- list(time=c(0), amount=100)
t1   <- seq(0, 120, by=0.1)
param1   <- c(V=1, Cl=0.1)

res1   <- pkmodel(time = t1, treatment = adm1, parameter = param1)

ggplot(data=res1, aes(x=time, y=cc)) + geom_line(size=1) +
  xlab("time (h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

### 1a. Patient's clearance decreases by 25%. 
##### (PK profile of 100 mg IV bolus (SD), CL = 0.075 L/hr, V= 1 L)
```{r}
adm1a <- list(time=c(0), amount=100)
t1a <- seq(0, 120, by=0.1)
param1a <- c(V=1, Cl=0.075)

res1a <- pkmodel(time = t1a, treatment = adm1a, parameter = param1a)

ggplot(data=res1a, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

### 1b. Patient's clearance decreases by 50%. 
##### (PK profile of 100 mg IV bolus (SD), CL = 0.05 L/hr, V = 1 L)
```{r}
adm1b <- list(time=c(0), amount=100)
t1b <- seq(0, 120, by=0.1)
param1b <- c(V=1, Cl=0.05)

res1b <- pkmodel(time = t1b, treatment = adm1b, parameter = param1b)

ggplot(data=res1b, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

### 1c. Overlay PK profiles of patient with normal clearance and decreased clearance 
##### (PK profile of 100 mg IV bolus (SD), V = 1 L, CL = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res1 %>% mutate(profile = "100mg SD"),
                              res1a %>% mutate(profile = "100mg SD, CL = 0.075 L/hr"),
                              res1b %>% mutate(profile = "100mg SD, CL = 0.05 L/hr"))

combined_output %>%
ggplot(aes(x = time, y = cc, color = factor(profile))) +
geom_line() + xlab("time(h)") + ylab("concentration (mg/L)") +
scale_color_discrete(name = "Clearance Changes") + theme_bw() + base_theme()
```

# 2. PK profile of 100 mg IV bolus administered every 6 hours
##### (PK profile of 100 mg IV bolus, LD (t = 0), MD (q= 6 hr), CL = 0.1 L/hr, V = 1 L)
```{r}
adm2 <- list(time=seq(0, 120, by = 6), amount=100)
t2 <- seq(0, 120, by=0.1)
param2 <- c(V=1, Cl=0.1)

res2 <- pkmodel(time = t2, treatment = adm2, parameter = param2)

ggplot(data=res2, aes(x=time, y=cc)) + geom_line(size=1) +
        xlab("time (h)") + ylab("concentration (mg/L)") +
        theme_bw() + base_theme()
```

### 2a. Patient's clearance decreases by 25%. 
##### (PK profile of 100 mg iv bolus, LD (t=0), MD (q=6hr), CL = 0.075 L/hr, V= 1 L)
```{r}
adm2a <- list(time=seq(0, 120, by = 6), amount=100)
t2a <- seq(0, 120, by=0.1)
param2a <- c(V=1, Cl=0.075)

res2a <- pkmodel(time = t2a, treatment = adm2a, parameter = param2a)

ggplot(data=res2a, aes(x=time, y=cc)) + geom_line(size=1) +
  xlab("time(h)") + ylab("concentration(mg/L)") +
  theme_bw() + base_theme()
```

### 2b. Patient's clearance decreases by 50%. 
##### (PK profile of 100 mg IV bolus, LD (t=0), MD (q=6hr), CL = 0.05 L/hr, V= 1 L)
```{r}
adm2b <- list(time=seq(0, 120, by = 6), amount = 100)
t2b <- seq(0, 120, by=0.1)
param2b <- c(V=1, Cl=0.05)

res2b <- pkmodel(time = t2b, treatment = adm2b, parameter = param2b)

ggplot(data=res2b, aes(x=time, y=cc)) + geom_line(size=1) +
  xlab("time(h)") + ylab("concentration(mg/L)") +
  theme_bw() + base_theme()
```

### 2c. Overlay PK profiles plot of patient with normal clearance and decreased clearance 
##### (PK profile of 100 mg IV bolus, LD(t=0), MD (q=6hr), V = 1 L, CL = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res2 %>% mutate(profile = "100mg Q6, CL = 0.1 L/hr"),
                              res2a %>% mutate(profile = "100mg Q6, CL = 0.075 L/hr"),
                              res2b %>% mutate(profile = "100mg Q6, CL = 0.05 L/hr"))
combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) + geom_line() +
  xlab("time(h)") + ylab("concentration (mg/L)") +
  scale_color_discrete(name = "Clearance Values") + theme_bw() + base_theme()
```

# 3. PK profile of 100 mg IV bolus given every 12 hours
##### (PK profile of 100 mg IV bolus, LD (t=0), MD (q=12 hr), CL =0.1 L/hr, V = 1 L)
```{r}
adm3 <- list(time=seq(0, 120, by = 12), amount = 100)
t3 <- seq(0, 120, by = 0.1)
param3 <- c(V=1, Cl=0.1)

res3 <- pkmodel(time = t3, treatment = adm3, parameter = param3)

ggplot(data=res3, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

### 3a. Patient's clearance decreases by 25%. 
##### (PK profile of 100 mg IV bolus, LD (t=0), MD (q=12hr), CL = 0.075 L/hr, V= 1 L)
```{r}
adm3a <- list(time=seq(0, 120, by = 12), amount = 100)
t3a <- seq(0, 120, by = 0.1)
param3a <- c(V=1, Cl=0.075)

res3a <- pkmodel(time = t3a, treatment = adm3a, parameter = param3a)

ggplot(data=res3a, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration (mg/L)") + theme_bw() + base_theme()
```

### 3b. Patient's clearance decreases by 50%. 
##### (PK profile of 100 mg IV bolus, LD (t=0), MD (q=12hr), CL = 0.05 L/hr, V= 1 L)
```{r}
adm3b <- list(time=seq(0, 120, by = 12), amount = 100)
t3b <- seq(0, 120, by = 0.1)
param3b <- c(V=1, Cl=0.05)

res3b <- pkmodel(time = t3b, treatment = adm3b, parameter = param3b)

ggplot(data=res3b, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```

### 3c. Overlay PK profiles of patient with normal clearance and decreased clearance 
##### (PK profile of 100 mg iv bolus, LD(t=0), MD (q=12hr), V = 1 L, CL = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res3 %>% mutate(profile = "100mg Q12, CL = 0.1 L/hr"),
                              res3a %>% mutate(profile = "100mg 12, CL = 0.075 L/hr"),
                              res3b %>% mutate(profile = "100mg Q12, CL = 0.05 L/hr"))
combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) + geom_line() +
  xlab("time(h)") + ylab("concentration (mg/L)") +
  scale_color_discrete(name = "Clearance Values") + theme_bw() + base_theme()
```

# 4. PK profile of 100 mg IV bolus administered every 24 hours
##### (PK profile of 100 mg IV bolus, LD (t=0), MD (q=24 hr), CL=0.1 L/hr, V = 1L)
```{r}
adm4 <- list(time=seq(0, 120, by = 24), amount = 100)
t4 <- seq(0, 120, by = 0.1)
param4 <- c(V=1, Cl=0.1)

res4 <- pkmodel(time= t4, treatment= adm4, parameter= param4)

ggplot(data=res4, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```

### 4a. Patient's clearance decreases by 25%. 
##### (PK profile of 100 mg IV bolus, LD (t=0), MD (q=24hr), CL = 0.075 L/hr, V= 1 L)
```{r}
adm4a <- list(time=seq(0, 120, by = 24), amount = 100)
t4a <- seq(0, 120, by = 0.1)
param4a <- c(V=1, Cl=0.075)

res4a <- pkmodel(time = t4a, treatment = adm4a, parameter = param4a)

ggplot(data=res4a, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```

### 4b. Patient's clearance decreases by 50%. 
##### (PK profile of 100 mg IV bolus, LD (t=0), MD (q=24hr), CL = 0.05 L/hr, V= 1 L)
```{r}
adm4b <- list(time=seq(0, 120, by = 24), amount = 100)
t4b <- seq(0, 120, by = 0.1)
param4b <- c(V=1, Cl=0.05)

res4b <- pkmodel(time = t4b, treatment = adm4b, parameter = param4b)

ggplot(data=res4b, aes(x=time, y=cc)) + geom_line(size=1) + xlab("time(h)") + ylab("concentration(mg/L)") + theme_bw() + base_theme()
```

### 4c. Overlay PK profiles of patient with normal clearance and decreased clearance
##### (PK profile of 100 mg iv bolus, LD(t=0), MD (q=24hr), V = 1 L, CL = 0.1 L/hr, 0.05 L/hr, 0.075 L/hr)
```{r}
combined_output <- bind_rows(res4 %>% mutate(profile = "100mg Q24, CL = 0.1 L/hr"),
                              res4a %>% mutate(profile = "100mg Q24, CL = 0.075 L/hr"),
                              res4b %>% mutate(profile = "100mg Q24, CL = 0.05 L/hr"))

combined_output %>%
  ggplot(aes(x=time, y=cc, color=factor(profile))) + geom_line() +
  xlab("time(h)") + ylab("concentration(mg/L)") +
  scale_color_discrete(name = "Clearance Values") + theme_bw() + base_theme()
```

# 5. Overlay plots of all dosing intervals
```{r}
combined_output <- bind_rows(res1 %>% mutate(profile = "100mg SD"),
                             res2 %>% mutate(profile = "100mg Q6"),
                             res3 %>% mutate(profile = "100mg Q12"),
                             res4 %>% mutate(profile = "100mg Q24"))


combined_output %>%
  ggplot(aes(x = time, y = cc, color = factor(profile))) +
  geom_line() + xlab("time(h)") + ylab("concentration (mg/L)") +
  scale_color_discrete(name = "Dosing Regimen") + theme_bw() + base_theme()
```

```{r}
devtools::session_info()
```